\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-03 paper.tex
updated section 4.2 and figures

\item Areas of Interest (AOI):  AOIs are those parts of the scene/screen that the experimenter wants to analyse the interaction (with the interface or with another user / robot). These AOIs are usually based on the hypotheses of the experiment. For example, if in a usability study of a phone advertisement \footnote{http://eyetracking.com.ua/eng/visualization/12.html} (Figure \ref{aoi}) the screen can divided into the model, the object and the caption. Once the screen has been divided into AOIs, we can compare the gaze distribution for different users and /or different experimental conditions.

@@

\item Heat-maps:

@@

\begin{enumerate}
\item Stationary target, stationary observer
\item Moving target, stationary observer
\item Stationary target, moving observer
\item Moving target, moving observer
\end{enumerate}

>>>>

\item Areas of Interest (AOI):  AOIs are those parts of the scene/screen that the experimenter wants to analyse the interaction (with the interface or with another user / robot). These AOIs are usually based on the hypotheses of the experiment. For example, if in a usability study of a phone advertisement \footnote{http://eyetracking.com.ua/eng/visualization/12.html} (Figure \ref{aoi}) the screen can divided into the advertisement model, the object and the caption. Once the screen has been divided into AOIs, we can compare the gaze distribution for different users and /or different experimental conditions.

@@

\item Heat maps: Heat maps are classical data visualisation tools. In terms of visualising eye-tracking data the heat maps show the distribution of the gaze. The distribution of the gaze then can be analysed for different user classes (for usability studies), experimental conditions or task based performance (Figures \ref{heatMapGood} and \ref {heatMapBad} \cite{sharma2014how}). The mathematical details about how to create the heat maps can be found in \cite{duchowski2007eye}.

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{heat-map-good-ex}
    \caption{Example heat map for a MOOC student who performed well in the posttest.
    source: \cite{sharma2014how}}
    \label{heatMapGood}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{heat-map-bad-ex}
    \caption{Example heat map for a MOOC student who performed poor in the posttest.
    source: source: \cite{sharma2014how}}
    \label{heatMapBad}
\end{figure}

@@

There are several use cases of mobile eye-tracking, we categorise them in following three categories:

\begin{enumerate}
\item Moving target, stationary observer
\item Stationary target, moving observer
\item Moving target, moving observer
\end{enumerate}

Next, we present an example of one of the use cases of mobile eye-tracking.
